---
title: "Lab 1 Team 6"
author: "Zhenzhen Chen, Jessica Kueon, Kellie McClernon"
date: "February 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Building a Book 



1. The last work for Chapter 15 is "Pseudo-class"!

2. Write a paragraph on the biggest problem you encountered when you were building the book, and how you managed to solve it.

We installed all the packakges we need to knit the file to html, but we keep getting the same error message in line 783 of Conditions.Rmd, "Error: 'error' inherits from 'warning/condition' not 'error_bad_argument".  
We could not solve the problem, so we tried knitting the file in a different laptop. Finally, we were able to knit it to html. 





```{r}
library(tidyverse) 
library(plotly)


weather <- read_fwf("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn-v2.5-stations.txt",
                    col_positions = fwf_positions(start = c(1, 3, 4, 6, 13, 22, 33, 39, 42, 73, 80, 87, 94), end = c(2, 3, 5, 11, 20, 30, 37, 40, 71, 78, 85, 92, 95), col_names = c("COUNTRY CODE", "NETWORK CODE ", "ID PLACEHOLDERS", "COOP ID", "LATITUDE", "LONGITUDE", "ELEVATION", "STATE", "NAME", "COMPONENT 1", "COMPONENT 2", "COMPONENT 3", "UTC OFFSET")))

weather <- weather %>%
  mutate(ELEVATION = as.numeric(ELEVATION))
# alternatively, you could use col_types = "ccccdddccccci" in the read_fwf() call

usa <- map_data("state")

statename <- data.frame(STATE = state.abb, region = tolower(state.name), stringsAsFactors = FALSE)

usa <- usa %>% 
  left_join(statename, by = "region") %>%
  left_join(unique(weather[c("STATE", "UTC OFFSET")]), by = "STATE")

theme_set(theme_light())

graphic <- weather %>%
  ggplot(aes(x = LONGITUDE, y = LATITUDE, fill = `UTC OFFSET`)) + 
  geom_polygon(data = usa, aes(x = long, y = lat, group = group)) +
  geom_path(data = usa, aes(x = long, y = lat, group = group), alpha = 0.3) +
  geom_point(aes(colour = ELEVATION)) + 
  scale_fill_gradient(low = "white", high = "grey") 



ggplotly(graphic)

```



# More weather data

The file `ushcn.tavg.latest.raw.tar.gz`
at ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5 contains data on average temperatures across the US. 

1. Download the file and get it to open with tools available in R. (Double-clicking is cheating! :) )

```{r gz_temp_file}
library(purrr)

# Setting paths to download files into on local computer
url <- "ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn.tavg.latest.raw.tar.gz"
path_zip <- "/home/kmc/Downloads/"
path_unzip <- "/home/kmc/temp_avg"
dfile <- "tavg.gz"

# download zip from online source into local directory
curl::curl_download(url, destfile = paste(path_zip, dfile, sep = "/"))

# unzip
untar(paste(path_zip, dfile, sep = "/"), exdir = path_unzip)

# list all files
folder <- list.files(path = path_unzip)
files <- list.files(path = paste(path_unzip, folder, sep = "/"))

# number of files in zipped folder
length(files)

## From previous part we can use the file of weather station names to find the ID for Fort Dodge.
# First we look at the structure of the station names and notice they are stored as all caps. Then we look for stations with DODGE in them and find only one, FORT DODGE IA. From the code book we know the file name we are looking for starts with the station ID which is stored in the first 4 columns of the weather name data. Finally we search the files for a file starting with that station ID.

head(weather$NAME)
fortdodge <- weather[str_which(weather$NAME, "DODGE"),]
ftd_tag <- paste0(fortdodge[1],fortdodge[2],fortdodge[3],fortdodge[4])
str_subset(files, ftd_tag)
```


2. Deliverable: include the number of files inside the file `ushcn.tavg.latest.raw.tar.gz` and the name of the file containing the temperature data of your home towns or Fort Dodge, IA (please specify). If things don't work write a paragraph on why things do not work and what you have tried.

The number of files inside the zipped folder are 1218. The name of the file containing Fort Dodge temperatures is "USH00132999.raw.tavg".
