---
title: "Lab 1 Team 6"
author: "Zhenzhen Chen, Jessica Kueon, Kellie McClernon"
date: "February 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Building a Book 

1. Write a paragraph on the biggest problem you encountered when you were building the book, and how you managed to solve it.

We installed all the packakges we need to knit the file to html, but we keep getting the same error message in line 783 of Conditions.Rmd, "Error: 'error' inherits from 'warning/condition' not 'error_bad_argument".  






```{r}
library(tidyverse)
station <- read_fwf("ushcn-v2.5-stations.txt", fwf_cols("COUNTRY CODE" == c(1,2), "NETWORK CODE" == c(3), "ID PLACEHOLDERS" == c(4,5), "COOP ID" == c(6:11), "LATITUDE" == c(13:20), "LONGITUDE" == c(22:30), "ELEVATION" == c(33:37), "STATE" == c(39,40), "NAME" == c(42:71)) )

?read_fwf
```



# More weather data

The file `ushcn.tavg.latest.raw.tar.gz`
at ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5 contains data on average temperatures across the US. 

1. Download the file and get it to open with tools available in R. (Double-clicking is cheating! :) )

```{r gz_temp_file}
library(purrr)

url <- "ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn.tavg.latest.raw.tar.gz"
path_zip <- "/home/kmc/Downloads/"
path_unzip <- "/home/kmc/temp_avg"
dfile <- "tavg.gz"

# download zip
curl::curl_download(url, destfile = paste(path_zip, dfile, sep = "/"))

#unzip
untar(paste(path_zip, dfile, sep = "/"), exdir = path_unzip)

# list all files
folder <- list.files(path = path_unzip)
files <- list.files(path = paste(path_unzip, folder, sep = "/"))

# number of files in folder
length(files)

# From previous part we can find that Fort Dodge is USH00132999.  And all files are of the form ###.raw.tavg
```


2. Deliverable: include the number of files inside the file `ushcn.tavg.latest.raw.tar.gz` and the name of the file containing the temperature data of your home towns or Fort Dodge, IA (please specify). If things don't work write a paragraph on why things do not work and what you have tried.

The number of files inside the zipped folder are 1218. The name of the file containing Fort Dodge temperatures is "USH00132999.raw.tavg".